Is Vagueness Beneficial for Hearers? \protect \\ Evidence from Experiments

### 2016-09-21 papers/2016-Special-Issue/v-special-issue-2016.tex
small change to general discussion, moved table too

Experiment 1 showed us that responses were faster and more accurate when the instructions were vague than when they were crisp, but the experiment could not distinguish effects of vagueness from those of number-avoidance or selection task: the vague conditions were also in verbal rather than numerical format; and mandated a comparison strategy rather than a matching strategy.  Experiment 2 showed us that number avoidance in the verbal format instructions is an important factor driving the faster response times in the task, and that vagueness does not have any additional explanatory power in either the verbal format instructions or the numerical format instructions when we generated verbal and numerical versions of both crisp and vague instructions. However the experiment could not distinguish benefits of number-avoidance in the verbal instructions from benefits of the comparison selection task: the verbal instructions also mandated a comparison strategy rather than a matching strategy. In experiments 3 and 4 we manipulated vagueness and the selection task independently of numerical format. We found that there are effects of the selection task mandated by the instruction, with the comparison task instructions attracting faster response times than the matching instructions, and that vagueness exerts benefits when the selection task is \emph{comparison}, but not when the task is \emph{matching}.

@@

@@

\begin{table}[htbp]
\caption{Vagueness as range reduction}
\begin{center}
\begin{tabular}{lll}
\hline
vagueness & selection task & candidates\\
\hline
crisp & matching & 1 candidate\\
crisp & comparison & 2 candidates\\
vague & matching & 2 candidates\\
vague & comparison & 1 candidate\\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}

>>>>

Experiment 1 showed us that responses were faster and more accurate when the instructions were vague than when they were crisp, but the experiment could not distinguish effects of vagueness from those of number-avoidance or selection task: the vague conditions were also in verbal rather than numerical format; and mandated a comparison strategy rather than a matching strategy.  Experiment 2 showed us that number avoidance in the verbal format instructions is an important factor driving the faster response times in the task, and that vagueness does not have any additional explanatory power in either the verbal format instructions or the numerical format instructions when we generated verbal and numerical versions of both crisp and vague instructions. 
% MJG edit
However the experiment could not distinguish benefits of number avoidance in the verbal instructions from benefits of 
the comparison selection task in the verbal instructions, since the verbal instructions mandated a comparison strategy, and the numeric instructions mandated a matching strategy. In experiments 3 and 4 we manipulated vagueness and the selection task separately at each level of numerical format. Across the two experiments, we found that there are effects of the selection task mandated by the instruction, with the comparison task instructions attracting faster response times than the matching instructions, and within the experiments we found that vagueness exerts benefits when the selection task is \emph{comparison}, but not when the task is \emph{matching}.

@@

\begin{table}[htbp]
\caption{Vagueness as range reduction: a summary of Experiments 3 and 4}
\label{Vagueness as range reduction}
\centering
\begin{tabular}{cccc}
selection task 				& vagueness		& candidates	& effect of vageueness	\\
\toprule
\multirow{ 2}{*}{comparison} 	& crisp 			& 2			& \multirow{ 2}{*}{vagueness advantage}  		\\
  						& vague			& 1			&                                               				\\
\midrule
\multirow{ 2}{*}{matching} 		& crisp 			& 1 			&\multirow{ 2}{*}{vagueness disadvantage}	\\
 						& vague			& 2			&								 	\\
\bottomrule
\end{tabular}
\end{table}

@@
